Project Setup

### 2024-09-18 setup.qmd
Fix typos

If you haven't already, open RStudio -- see @nte-terminal for an alternative to RStudio. Then, click on _File_ > _New Project..._ to open the _New Project Wizard_.

@@

Then, one can open an R session, by simply typing `R` into the terminal. Next, sure that `getwd()` indicates that the working directory is `code-publishing-exercise`. If not, set it using `setwd("code-publishing-exercise")`. Then, initialize `renv`:

@@

A human-readable data dictionary is necessary for making one's research reproducible and the example we provided demonstrates only the bare minimum. A full data documentation including measurement instruments, sampling procedures, appropriate weighting, contact information, and more information about the study can be created with the R package [`pointblank`](https://rstudio.github.io/pointblank/articles/INFO-1.html). And one could go even further by making the information machine-readable in a standardized way. We provide an optional example of that in @nte-frictionless. If you want to learn more about the sharing of research data, have a look at the tutorial "[FAIR Research Data management](https://lmu-osc.github.io/FAIR-Data-Management/)".

>>>>

If you haven't already, open RStudio -- see @nte-terminal for how to use the terminal instead. Then, click on _File_ > _New Project..._ to open the _New Project Wizard_.

@@

Then, one can open an R session, by simply typing `R` into the terminal. Next, make sure that `getwd()` indicates that the working directory is `code-publishing-exercise`. If not, set it using `setwd("code-publishing-exercise")`. Then, initialize `renv`:

@@

A human-readable data dictionary is necessary for making one's research reproducible and the example we provided demonstrates only the bare minimum. A full data documentation including measurement instruments, sampling procedures, appropriate weighting, contact information, and more information about the study can be created with the R package [`pointblank`](https://rstudio.github.io/pointblank/articles/INFO-1.html). And one could go even further by making the information machine-readable in a standardized way. We provide an optional example of that in @nte-frictionless. If you want to learn more about the sharing of research data, have a look at the tutorial "[FAIR research data management](https://lmu-osc.github.io/FAIR-Data-Management/)".
